Leadership across cultures and contexts: an exploratory analysis

### 2020-04-15 leadership_across_cultures_contexts.Rmd
Minor edits in ms.

<!-- BENEFITS: 'MODEL' OF POTENTIAL BENEFIST -->
@von_rueden_leadership_2015 review a large body of theory and ethnography and outline four possible mechanisms by which leaders in small-scale societies might offset the potential costs associated with various leadership roles; leaders may, (1) facilitate collective actions that yield net benefits to themselves or their close kin; (2) claim a fee for their services, such a tax or greater share of returns; (3) receive reciprocal exchange in other currencies from followers who have benefited from their services; or (4) gain other social or reproductive benefits by signaling their high quality as a mate and social partner.

>>>>

<!-- BENEFITS: 'MODEL' OF POTENTIAL BENEFIST -->
@von_rueden_leadership_2015 review a large body of theory and ethnography and outline four possible mechanisms by which leaders in small-scale societies might offset the potential costs associated with various leadership roles; leaders may, (1) facilitate collective actions that yield net benefits to themselves or their close kin; (2) claim a fee for their services, such as a tax or greater share of returns; (3) receive reciprocal exchange in other currencies from followers who have benefited from their services; or (4) gain other social or reproductive benefits by signaling their high quality as a mate and social partner.
